Learning Discrete Bayesian Networks from Continuous Data

### 2016-08-09 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
appendix

\section*{Appendix}
\label{sec:appendix}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix A}

This section provides a counterexample of marginal discretization methods. Different from more principled methods, as such the MDL discretization or the proposed Bayesian approach, the marginal discretization methods ignore the dependency of data samples between different variables. Therefore, it might lead to worse discretization outcomes. Here is an example: consider a synthetic dataset with two variable $A$ and $B$, with $500$ data samples generated by the Bayesian network $A \rightarrow B$ and the probability distribution shown in Table \ref{table:marginal_counter}. Following the experiment procedure in Section \ref{sec:experiments}, both the MDL method and the proposed Bayesian approach find a discretization edge of $B$ around $1.0$ and have log likelihood $-0.023$. On the other hand, while discretizing variable $B$ based on its marginal distribution of samples, the Bayesian block and other marginal discretization can not locate a discretization edge and result in log likelihood $-0.69$. This example shows that the discretization method without considering the dependency between variables might lead to fatal outcomes.

\begin{table}[ht]
	\centering
	\caption{Probability distributions for the variables in the network $A \rightarrow B$, in which $A$ is a discrete variable and $B$ is a continuous one
	}
	\label{table:marginal_counter}
	\begin{tabular}{cl}
		\toprule
		Variable               & Distribution                                   \\ \midrule
		\multirow{2}{*}{$A$}&$P(a^1) = 0.5$     \\
		& $P( a^2) = 0.5$     \\ \midrule

		\multirow{2}{*}{$B$} & $p(b \mid A = a^1 \sim U[0,1]$\\
		& $p(b \mid A = a^2 \sim U[1,2]$\\
		\bottomrule
	\end{tabular}
\end{table}

\section*{Appendix B}
\label{sec:appendix}
